### 2015-03-06 ThesisJo/derivations.tex
la2pdf commit - 2015:03:06	20:01:38	(Fri 6.Mar)

Now let us choose a trigonometric window function:
%
\begin{align}
\w = e^{j\phi_\theta[m]}\frac{1}{2\pi\alpha?}\big(\alpha + (1-\alpha)\sin\left(\frac{2\pi m}{M-1}\right)\big)
\end{align}
%
where $\phi_\theta[m] = \frac{2\pi}{\lambda}dm\sin\theta$. Inserting this yields:
%
\begin{align}
\w\H\x &= \sumb{m=0}{M-1} e^{j\phi_\theta[m]}\Big(\alpha + (1-\alpha)\sin\left(\frac{2\pi m}{M-1}\right)\Big) x_m^* \nn
&= \alpha\sumb{m=0}{M-1} e^{j\phi_\theta[m]} x_m^* + (1-\alpha)\sumb{m=0}{M-1} e^{j\varphi[m]}\sin\left(\frac{2\pi m}{M-1}\right) x_m^* \\
&= \alpha \a + (1-\alpha)\b
\end{align}
%
where:
%
\begin{align}
a = \sumb{m=0}{M-1} e^{j\phi_\theta[m]}x_m^* \qquad \text{and} \qquad b_m = \sumb{m=0}{M-1} e^{j\phi_\theta[m]}\sin\left(\frac{2\pi m}{M-1}\right)x_m^*
\end{align}
%
where
%
\begin{align}
|\w\H\x|^2 &= \Big| \alpha a + (1-\alpha)b \Big|^2 \nn
&= \Big[\alpha a + (1-\alpha)b\Big] \Big[\alpha a^* + (1-\alpha)b^*\Big] \nn
&= \alpha^2 aa^* + \alpha a(1-\alpha)b^* + \alpha a^*(1-\alpha)b + (1-\alpha)^2bb^* \nn
&= \alpha^2 aa^* + \alpha(1-\alpha)(ab^* + a^*b) + (1-\alpha)^2bb^* \nn
\end{align}
%

>>>>

Now let us choose a trigonometric window function:
%
\begin{align}
\w = e^{j\phi_\theta[m]}\frac{1}{2\pi\alpha?}\big(\alpha + (1-\alpha)\sin\left(\frac{2\pi m}{M-1}\right)\big)
\end{align}
%
where $\phi_\theta[m] = \frac{2\pi}{\lambda}dm\sin\theta$. Inserting this yields:
%
\begin{align}
\w\H\x &= \sumb{m=0}{M-1} e^{j\phi_\theta[m]}\Big(\alpha + (1-\alpha)\sin\left(\frac{2\pi m}{M-1}\right)\Big) x_m^* \nn
&= \alpha\sumb{m=0}{M-1} e^{j\phi_\theta[m]} x_m^* + (1-\alpha)\sumb{m=0}{M-1} e^{j\varphi[m]}\sin\left(\frac{2\pi m}{M-1}\right) x_m^* \\
&= \alpha \a + (1-\alpha)\b
\end{align}
%
where:
%
\begin{align}
a = \sumb{m=0}{M-1} e^{j\phi_\theta[m]}x_m^* \qquad \text{and} \qquad b_m = \sumb{m=0}{M-1} e^{j\phi_\theta[m]}\sin\left(\frac{2\pi m}{M-1}\right)x_m^*
\end{align}
%
where
%
\begin{align}
|\w\H\x|^2 &= \Big| \alpha a + (1-\alpha)b \Big|^2 \nn
&= \Big[\alpha a + (1-\alpha)b\Big] \Big[\alpha a^* + (1-\alpha)b^*\Big] \nn
&= \alpha^2 aa^* + \alpha a(1-\alpha)b^* + \alpha a^*(1-\alpha)b + (1-\alpha)^2bb^* \nn
&= \alpha^2 aa^* + \alpha(1-\alpha)(ab^* + a^*b) + (1-\alpha)^2bb^* \nn
&= \alpha^2 (aa^* - (ab^* + a^*b) - bb^*) + \alpha(ab^* + a^*b) + bb^* \nn
\end{align}
%
